\documentclass[margin]{res}
\setlength{\textwidth}{5.1in}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Jeffrey Lund}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
\moveleft.5\hoffset\centerline{jefflund@gmail.com}
\moveleft.5\hoffset\centerline{(425) 306-0496}

\begin{resume}

\section{Education}

Ph.D. in Computer Science, Brigham Young University\\
Graduation: April 2019 ~ GPA: 4.0\\
Dissertation: Fine-Grained Topic Models Using Anchor Methods

M.S. in Computer Science, Brigham Young University\\
Graduated: December 2015 ~ GPA: 4.0\\
Thesis: Fast Inference for Interactive Models of Text

B.S. in Computer Science, Brigham Young University\\
Graduated: Magna Cum Laude April 2011 ~ GPA: 3.9\\
Minor: Mathematics

Relevant Graduate Coursework: Natural Language Processing, Bayesian Statistics,
Machine Learning, Artificial Intelligence, Data Mining, Deep Learning

\section{Languages and Tools}
Python, Go, C++, Java\\
Git, Unix toolchain

\section{Experience}

Software Engineer, Google LLC \hfill Jan 2019 - Present
\begin{itemize} \itemsep -2pt
\item Worked with models for click-through rate prediction on google.com
\item Improved model reproducibility using transfer learning
\end{itemize}

Research Assistant, BYU Applied Machine Learning Lab \hfill Sept 2011 - Dec 2018
\begin{itemize}  \itemsep -2pt
\item Organized and led topic modeling group at BYU
\item Implemented novel interactive topic models for document classification
\item Taught CS 142 Introduction to Computer Programming
\end{itemize}

Engineering Intern, Google Inc. \hfill April 2015 - June 2015
\begin{itemize} \itemsep -2pt
\item Improved accuracy of DoubleClick conversion rate prediction by integrating topic-based signals from Rephil into prediction pipeline
\item Demonstrated bid optimization improvements using topic-based conversion rate prediction
\end{itemize}

Engineering Intern, Google Inc. \hfill May 2013 - Aug 2013
\begin{itemize} \itemsep -2pt
\item Worked on Rephil team, which is a web scale noisy-OR based topic model
\item Added to suite of tools used by Rephil team for model comparison
\item Designed and implemented methodology for automatically detecting harmful model updates in incrementally trained Rephil models
\end{itemize}

Intern, LucidChart Inc. \hfill May 2012 - Aug 2012
\begin{itemize} \itemsep -2pt
\item Designed and implemented high volume automated mailing services
\item Implemented notification system which delivers alerts from critical services
\end{itemize}

Edison Identification Intern, GE Energy \hfill May 2011 - Aug 2011
\begin{itemize} \itemsep -2pt
\item Enhanced capabilities of entity modeling framework, used in various diagnostic tools for large turbines
\item Rewrote entity model serialization, greatly improving performance at the core of the GE Energy framework
\end{itemize}

Research Assistant, BYU Natural Language Processing Lab \hfill Sept 2010 - Apr
2011
\begin{itemize} \itemsep -2pt
\item Implemented various visualizations of topic models for Topical Browser
\end{itemize}

Teaching Assistant, Algorithm Analysis \hfill Jan 2011 - Apr 2011
\begin{itemize} \itemsep -2pt
\item Helped students understand various algorithms used in class projects
\end{itemize}

Teaching Assistant, Artificial Intelligence \hfill Sept 2010 - Dec 2010
\begin{itemize} \itemsep -2pt
\item Mentored students by teaching help sessions and consulting with project teams
\end{itemize}

Student Programmer, BYU Print and Mail \hfill Sept 2008 - Aug 2010
\begin{itemize} \itemsep -2pt
\item Implemented automated order placement, tracking and billing system
\end{itemize}

% XXX last few are blah?

\section{Publications}

Jeffrey Lund, Piper Armstrong, Wilson Fearn, Stephen Cowley, Courtni Byun, Jordan Boyd-Graber and Kevin Seppi. Automatic Evaluation of Local Topic Quality. Association for Computational Linguistics, 2019

Jeffrey Lund, Piper Armstrong, Wilson Fearn, Stephen Cowley, Emily Hales and Kevin Seppi. Cross-referencing Using Fine-grained Topic Modeling. North American Association for Computational Linguistics, 2019

Jeffrey Lund, Stephen Cowley, Wilson Fearn, Emily Hales and Kevin Seppi. Labeled Anchors and a Scalable, Transparent, and Interactive Classifier. Empirical Methods in Natural Language Processing, 2018

Jeffrey Lund and Yiu-Kai Ng. Movie Recommendations Using a Deep Learning Approach. International Conference on Information Reuse and Integration, 2018

Jeffrey Lund, Connor Cook, Kevin Seppi and Jordan Boyd-Graber. Tandem Anchoring: A Multiword Anchor Approach for Interactive Topic Modeling. Association for Computational Linguistics, 2017

You Lu, Jeffrey Lund and Jordan Boyd-Graber. Why ADAGRAD Fails for Online Topic Modeling. Empirical Methods in Natural Language Processing, 2017

Jeffrey Lund, Chace Ashcroft, Andrew McNabb and Kevin Seppi. Mrs: High Performance MapReduce for Iterative and Asynchronous Algorithms in Python. Python for High-Performance and Scientific Computing, 2016

Jeffrey Lund, Paul Felt, Kevin Seppi and Eric Ringger. Fast Inference for Interactive Models of Text. International Conference on Computational Linguistics, 2016

Thang Nguyen, Jordan Boyd-Graber, Jeffrey Lund, Kevin Seppi and Eric Ringger. Is Your Anchor Going Up or Down? Fast and Accurate Supervised Topic Models. North American Association for Computational Linguistics, 2015

Andrew McNabb, Jeffrey Lund and Kevin Seppi. Mrs: MapReduce for Scientific Computing in Python. Python for High-Performance and Scientific Computing, 2012

Matthew Gardner, Joshua Lutes, Jeffrey Lund, Joshua Hansen, Daniel Walker, Eric Ringger and Kevin Seppi. The Topic Browser An Interactive Tool for Browsing Topic Models. NIPS Workshop on Challenges of Data Visualization, 2010

\end{resume}
\end{document}
